Temporal Split

### 2023-01-24 workflow/notebooks/temporal-split.Rmd
Write code to get boostrap CI for temporal split

>>>>

## try bootstrapping with rsample

```{r boot}
library(furrr)
library(mikropml)
library(rsample)

model <- readRDS(here('results/predict_idsa/taxlevel_OTU/metric_AUC/dataset_int/trainfrac_0.8/temporal-split/glmnet_100_model.Rds'))

test_dat <- read_csv(here('results/predict_idsa/taxlevel_OTU/metric_AUC/dataset_int/trainfrac_0.8/temporal-split/glmnet_100_test-data.csv'))

calc_perf <- function(split) {
   get_performance_tbl(
        model,
        split$data,
        outcome_colname = 'idsa',
        perf_metric_function = caret::twoClassSummary,
        perf_metric_name = 'AUC',
        class_probs = TRUE,
        method = 'glmnet',
        seed = 100
      ) %>% 
    select(-c(method, seed)) %>% 
    pivot_longer(everything(), names_to = 'term', values_to = 'estimate')
}

boots <- bootstraps(test_dat, times = 10) %>% 
  mutate(perf = future_map(splits, ~ calc_perf(.x)))

int_pctl(boots, perf)
```
